2 Party State Assertion Channels

### 2019-01-12 paper/main.tex
Added paper

\begin{figure}[H]
	\begin{boxedminipage}{\columnwidth}
		\begin{tabular}{l}
			\contract StateAssertionChannel \{ \\
			\quad $\enum$ Status \{$\DEPOSIT$, $\ON$, $\DISPUTE$\} \\
			\quad Status status; $\uintno$ deadline; $\hashblue$ hstate, $\uintno$ i; $\addr$ firstturn; \\ %\comment{// Latest state info}  \\
			\quad $\addr$ asserter; $\hashblue$ prevstate; $\bytes$ input; $\uintno$ cmd;\\
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ setstate($\bytes[]$ \_sigs, $\uintno$ \_i, $\addr$ \_turn, $\hashblue$ \_newstate) \{ \\
			\quad \quad \require(\_i $>$ i)); \comment{ // Largest counter so far} \\
			\quad \quad $\hashblue$ hmsg = hash(\_i, \_newstate,\_turn, $\addr(\this)$);  \\
			\quad \quad \require(verifySigs(hmsg, sigs, plist));  \comment{// Everyone signed new hstate} \\
			\quad \quad status = Dispute.\ON; refundAllBonds(); \comment{// Cancel dispute and refund bonds} \\
			\quad \quad bestRound = \_i; hstate = \_newstate;  firstturn = \_turn; \comment{// Agreed state} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ triggerDispute() \{ \\
			\quad \quad $\require$(status == Status.ON \& onlyParties()); \\
			\quad \quad  status = Status.DISPUTE; \\
			\quad \quad deadline = now + disputePeriod; \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ assertState($\hashblue$ \_prevstate, $\hashblue$ \_newstate, $\bytes$ input, $\uintno$ cmd) \{ \\
			\quad \quad $\require$(status == Status.DISPUTE); \\
			\quad \quad $\require$(\_prevstate == hstate \&\& checkCallerTurn()) \\ 
			\quad \quad asserter = $\msgsender$; \comment{// Store name of asserter} \\ 
			\quad \quad prev\_hstate = \_prevstate; hstate = \_newstate; \\ 
			\quad \quad input = \_input; cmd = \_cmd; \\
			\quad \quad deadline = now + disputePeriod; \comment{// Reset deadline after an assertion} \\
			\quad \}

		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ challengeAssertion($\bytes$ \_oldstate) \{ \\
			\quad \quad \require(status == Status.DISPUTE); \\
			\quad \quad \require(asserter != $\msgsender$); \comment{// Stop self-challenging} \\
			\quad \quad \require(prev\_hstate == hash(\_oldstate)); \comment{// Verify old state is correct} \\
			\quad \quad $\hashblue$ temphstate = $\appblue.\transitionblue$(asserter, \_oldstate, input, cmd); \\ 
			\quad \quad $\ifs$(hstate != temphstate) \{ \comment{// Send all coins and bond to non-cheater.}  \} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ timeOut() \{ \\
			\quad \quad \require(now $>=$ deadline \&\& status == Status.dispute); \\ 
			\quad \quad \comment{// Send all coins/bonds to asserter (i.e. last party to respond).} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ resolve($\uintno$ balance1, $\uintno$ balance2) \{ \\
			\quad \quad $\ifs$(status == Status.Dispute) \{ \\
			\quad \quad \quad $\require$(checkCallerTurn()); \comment{// Let non-asserter challenge or resolve.} \\
			\quad \quad \} $\elses$ \{ \require(status == Status.ON); \} \comment{// No on-going dispute.} \\ 
			\quad \quad $\require$(hstate == hash(balance1, balance2)); \comment{// Terminal state?} \\
			\quad \quad \comment{// Send each party their final balance.} \\
			\quad \}
		\end{tabular}

	   	\begin{tabular}{l}
	   		\quad $\oninput$ deposit(); \comment{// Not implemented due to space} \\
	   		\quad $\oninput$ onlyParties() $\returns(\bool)$; \comment{// Check if tx signer is whitelisted} \\
	   		\quad $\oninput$ refundAllBonds() $\internal$; \comment{// Refunds all bonds} \\
	   		\quad $\oninput$ checkCallerTurn() $\returns$($\bool$); \comment{Enforce turn based disputes} \\
	   		\quad $\oninput$ verifySigs($\bytes$ hmsg, $\bytes[]$ sigs, $\addr[]$ signers) $\returns(\bool)$; \\
	   		\}
	   \end{tabular}
	\end{boxedminipage}

>>>>

\begin{figure}[H]
	\begin{boxedminipage}{\columnwidth}
		\begin{tabular}{l}
			\contract StateAssertionChannel \{ \\
			\quad $\enum$ Status \{$\DEPOSIT$, $\ON$, $\DISPUTE$\}, $\addr$[] plist; \\
			\quad Status status; $\uintno$ deadline; $\hashblue$ $\hstatei$, $\uintno$ i; $\addr$ turn; \\ %\comment{// Latest state info}  \\
			\quad $\addr$ asserter; $\hashblue$ $\hstateplus$; $\bytes$ input; $\uintno$ cmd; $\bool$ assertion; \\
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ setstate($\bytes[]$ \_sigs, $\uintno$ \_i, $\addr$ \_turn, $\hashblue$ \_$\hstatei$) \{ \\
			\quad \quad \require(\_i $>$ i)); \comment{ // Largest counter so far} \\
			\quad \quad $\hashblue$ hmsg = hash(\_i, \_$\hstatei$,\_turn, $\addr(\this)$);  \\
			\quad \quad \require(verifySigs(hmsg, sigs, plist));  \comment{// Everyone signed new hstate} \\
			\quad \quad delete(input,cmd,\hstateplus,asserter, assertion); \comment{// Delete assertion}\\
			\quad \quad status = Status.\ON; i = \_i; $\hstatei$ = \_$\hstatei$;  turn = \_turn; \comment{// Agreed state} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ triggerDispute() \{ \\
			\quad \quad $\require$(status == Status.ON \& onlyParties()); \comment{// Only parties trigger} \\
			\quad \quad  status = Status.DISPUTE; deadline = now + disputePeriod;\\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ assertState($\hashblue$ \_$\hstatei$, $\hashblue$ \_$\hstateplus$, $\bytes$ \_input, $\uintno$ \_cmd) \{ \\
			\quad \quad $\require$(status == Status.DISPUTE \texttt{AND} checkCallerTurn()); \\
			\quad \quad $\ifs($!assertion)  \{ \\ 
			\quad \quad \quad assertion = true; $\require(\hstatei == \_\hstatei)$ \comment{// First assertion}  \\ 
			\quad \quad \} $\elses$ \{ $\require$($\hstateplus$ == \_$\hstatei$); \} \comment{// Extending existing assertion} \\ 
			\quad \quad asserter = $\msgsender$; input = \_input; cmd = \_cmd; \comment{// Store assertion} \\
			\quad \quad $\hstatei$ = $\hstateplus$; $\hstateplus$ = \_$\hstateplus$; \comment{// i accepted. i+1 assertion} \\ 
			\quad \quad deadline = now + disputePeriod; \comment{// Reset deadline after an assertion} \\
			\quad \}

		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ challengeAssertion($\bytes$ \_oldstate) \{ \\
			\quad \quad \require(status == Status.DISPUTE); \require(asserter != $\msgsender$);  \\
			\quad \quad \require($\hstatei$ == hash(\_oldstate) AND assertion); \comment{// Assertion exists} \\
			\quad \quad $\hashblue$ checkh = $\appblue.\transitionblue$(asserter, \_oldstate, input, cmd); \comment{// Compute} \\ 
			\quad \quad $\ifs$($\hstateplus$ != checkh) \{ \comment{// Send all coins and bond to non-cheater.}  \} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ timeOut() \{ \\
			\quad \quad \require(now $>=$ deadline \&\& status == Status.dispute); \\ 
			\quad \quad \comment{// Send all coins/bonds to asserter (i.e. last party to respond).} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ resolve($\uintno$ balance1, $\uintno$ balance2) \{ \\
			\quad \quad $\ifs$(status == Status.Dispute) \{ \\
			\quad \quad \quad $\require$(checkCallerTurn()); \comment{// Non-asserter must resolve b4 timeout.} \\
			\quad \quad \} $\elses$ \{ \require(status == Status.ON); \} \comment{// No on-going dispute.} \\ 
			\quad \quad $\require$(hstate == hash(balance1, balance2)); \comment{// Terminal state?} \\
			\quad \quad \comment{// Send each party their final balance and bond.} \\
			\quad \}
		\end{tabular}

	   	\begin{tabular}{l}
	   		\quad $\oninput$ deposit(); \comment{// Not implemented due to space - INCLUDES BOND} \\
	   		\quad $\oninput$ onlyParties() $\returns(\bool)$; \comment{// Check if tx signer is whitelisted} \\
	   		\quad $\oninput$ refundAllBonds() $\internal$; \comment{// Refunds all bonds} \\
	   		\quad $\oninput$ checkCallerTurn() $\returns$($\bool$); \comment{Enforce turn based disputes} \\
	   		\quad $\oninput$ verifySigs($\bytes$ hmsg, $\bytes[]$ sigs, $\addr[]$ signers) $\returns(\bool)$; \\
	   		\}
	   \end{tabular}
	\end{boxedminipage}
